Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-12-10 ms.tex
adding temperature corrections

\begin{figure*}
{\gridline{\fig{azlab08_sub320_multiexp_temp_correlation.pdf}{0.48\textwidth}{Sub 320 Multi-exposure test}
\fig{azlab08_sub320_lakeshore_tchange_temp_correlation.pdf}{0.48\textwidth}{Lakeshore Temp Change}}}
\caption{Two separate time series show the same correlation with Box Temperature after removing the 4.9 hour time offset}
\end{figure*}

>>>>

\begin{figure*}
{\gridline{\fig{azlab08_sub320_multiexp_temp_correlation.pdf}{0.48\textwidth}{Sub 320 Multi-exposure test}
\fig{azlab08_sub320_lakeshore_tchange_temp_correlation.pdf}{0.48\textwidth}{Lakeshore Temp Change}}}
\caption{Two separate time series show the same correlation with Box Temperature after removing the 4.9 hour time offset}\label{fig:LEDTcorrelation}
\end{figure*}

\begin{figure*}
{\gridline{\fig{azlab08_sub320_multiexp_corrected.pdf}{0.48\textwidth}{Sub 320 Multi-exposure test}
\fig{azlab08_sub320_lakeshore_tchange_corrected.pdf}{0.48\textwidth}{Lakeshore Temp Change}}}\label{fig:LEDTcorrection}
\caption{After removing the 4.9 hour time offset and a linear trend with temperature, the fluctuations are greatly reduced.}
\end{figure*}
